Finding Bugs in JavaScript Engines with Differential Testing

### 2018-07-18 docs/google-research-awards-latam/main.tex

\begin{wrapfigure}[10]{r}[0pt]{0.45\textwidth}
  \vspace{-5ex}
  \centering
  \includegraphics[trim=20 350 200 0,clip,width=0.45\textwidth]{google-awards-workflow}
  \caption{\label{fig:workflow}Fuzzing Infrastructure.}
  \vspace{-5ex}  
\end{wrapfigure}
Fuzzing is a popular technique to generate new test inputs from
existing inputs~\cite{fuzz-testing-history} with the typical goal of
finding crashes. Several fuzzing methods have been proposed in the
past, varying with respect to how new inputs are generated (\eg{},
coverage-based~\cite{afl,honggfuzz},
grammar-based~\cite{grammarinator,jsfunfuzz}, and
random-based~\cite{radamsa}). Figure~\ref{fig:workflow} shows a generic pipeline of a
fuzzer infrastructure, instantiated to our problem. Arrows indicate data flow; lines
with no arrow denote encapsulation. In our case, JS files are
provided as seeds to bootstrap the process. These files can
originate from the test suites of the engine codebases or from the bug
reports in their issue trackers. The fuzzing infrastructure selects
randomly one of the inputs to fuzz with a given tool, say the
black-box fuzzer Radamsa~\cite{radamsa}. Each fuzzing iteration
produces a new file. For grammar-agnostic fuzzers, like Radamsa, the
infrastructure can discard syntactically invalid
inputs using an external parser for the input language; semantically
invalid inputs can be prevented with with linters. Once the input is
found to be likely valid, the infrastructure
invokes the oracle to check correctness. In case all engines
consider the test output consistent (\ie{}, all pass or all fail), the
infrastructure discards the corresponding input. Otherwise, it considers that
input as potentially fault-revealing and interesting. Currently, we
classify alarms in the HI and LO groups. The HI group includes
those warnings that manifest execution errors spawned directly by the
test (or its close neighborhood) whereas the LO group includes the
rest of the warnings. \Igor{We found empirically that 88\% of the
issues reported are included in the HI group and 58\% of them was confirmed}.

@@

The workflow described in Section~\ref{sec:design} is currently
functional. This section shows preliminary results obtained with our
infrastructure providing some evidence that finding bugs in JS runtime
engines with differential testing is promising. Table~\ref{tab:bugs} shows the list of bugs we
reported on issue trackers of different engines in the period of 42 days. For example, bug \# 6 was manifested by the JS code \CodeIn{var
  a = \{valueOf:~function()\{return ``\textbackslash{}x00''\}\}
  assert(+a === 0)\}}.  The object property \CodeIn{valueOf} stores a
function that returns a primitive value identifying the target
object~\cite{valueof}. That function returns an empty string in the
original version of this code. The modified version of the code
returns a string representation of a null character (called
\CodeIn{NUL} in ascii).
\Igor{The unary plus expression ``\CodeIn{+a}", appearing in the assertion,
is equivalent to the abstract operation \CodeIn{ToNumber(a.valueOf())}
that converts a string to a number, otherwise the operation returns NaN 
(Not a Number)\cite{unary-plus}}. For this case, \Igor{isto esta correto? $\rightarrow$ all engines but} Chakra evaluate the unary
plus to NaN as expected, as the null character cannot be converted. As result, the test fails as
expected. Chakra, in contrast, incorrectly converts the string to zero, making the test to pass.

So far, ten of the bugs we reported
were confirmed, two of which were fixed. One bug report we
submitted was rejected on the basis that the offending JS file
manifested an expected incompatibility across engine
implementations.
Note from the table that all bug
reports still waiting for confirmation are associated with the
JavaScriptCore engine (JSC). A closer look at the JSC issue tracker
showed that the triage process is very slow for that engine. As of
now, we did not find any new bug on SpiderMonkey and V8; the bugs we
found were duplicates and were not reported. Finally, it is
worth noting that \Igor{7 out of 17} JS files that manifested
discrepancies were \emph{not} produced with fuzzing (column
``Fuzz''). These are test files from suites of different engines. This
observation emphasizes the importance of continuously collecting test suites from
multiple sources; today, we use test suites from seven different open
source engines, including a total of 30K test files.

@@

%%  LocalWords:  d'Amorim oes Jornalista Fernandes JS Patra Pradel
%%  LocalWords:  fuzzer runtime WebAssembly's codebases Radamsa JSC
%%  LocalWords:  fuzzers linters JavaScriptCore SpiderMonkey AFL NUL
%%  LocalWords:  HonggFuzz jsfunfuzz Grammarinator WebAssembly ascii
%%  LocalWords:  valueOf unary NaN Chakra cccccc Url JavascriptCore
%%  LocalWords:  cgi tmp

>>>>

\begin{wrapfigure}[10]{r}[0pt]{0.45\textwidth}
  \vspace{-5ex}
  \centering
  \includegraphics[trim=20 350 200 0,clip,width=0.45\textwidth]{google-awards-workflow}
  \caption{\label{fig:workflow}Fuzzing Infrastructure.}
  \vspace{-5ex}  
\end{wrapfigure}
Fuzzing is a popular technique to generate new test inputs from
existing inputs~\cite{fuzz-testing-history} with the typical goal of
finding crashes. Several fuzzing methods have been proposed in the
past, varying with respect to how new inputs are generated (\eg{},
coverage-based~\cite{afl,honggfuzz},
grammar-based~\cite{grammarinator,jsfunfuzz}, and
random-based~\cite{radamsa}). Figure~\ref{fig:workflow} shows a generic pipeline of a
fuzzer infrastructure, instantiated to our problem. Arrows indicate data flow; lines
with no arrow denote encapsulation. In our case, JS files are
provided as seeds to bootstrap the process. These files can
originate from the test suites of the engine codebases or from the bug
reports in their issue trackers. The fuzzing infrastructure selects
randomly one of the inputs to fuzz with a given tool, say the
black-box fuzzer Radamsa~\cite{radamsa}. Each fuzzing iteration
produces a new file. For grammar-agnostic fuzzers, like Radamsa, the
infrastructure can discard syntactically invalid
inputs using an external parser for the input language; semantically
invalid inputs can be prevented with with linters. Once the input is
found to be likely valid, the infrastructure
invokes the oracle to check correctness. In case all engines
consider the test output consistent (\ie{}, all pass or all fail), the
infrastructure discards the corresponding input. Otherwise, it considers that
input as potentially fault-revealing and interesting. Currently, we
classify alarms in the HI and LO groups. The HI group includes
those warnings that manifest execution errors spawned directly by the
test (or its close neighborhood) whereas the LO group includes the
rest of the warnings. We found that 88\% of the
issues reported are from the HI group.

@@

The workflow described in Section~\ref{sec:design} is currently
functional. This section shows preliminary results obtained with our
infrastructure providing some evidence that finding bugs in JS runtime
engines with differential testing is promising. Table~\ref{tab:bugs} shows the list of bugs we
reported on issue trackers of different engines in the period of 42 days. For example, bug \# 6 was manifested by the JS code \CodeIn{var
  a = \{valueOf:~function()\{return ``\textbackslash{}x00''\}\}
  assert(+a === 0)\}}.  The object property \CodeIn{valueOf} stores a
function that returns a primitive value identifying the target
object~\cite{valueof}. That function returns an empty string in the
original version of this code. The modified version of the code
returns a string representation of a null character (called
\CodeIn{NUL} in ascii). The unary plus expression ``\CodeIn{+a}", appearing in the assertion,
is equivalent to the abstract operation \CodeIn{ToNumber(a.valueOf())}
that converts a string to a number, otherwise the operation returns NaN 
(Not a Number)\cite{unary-plus}. For this case, Chakra evaluates the unary
plus to NaN as expected, as the null character cannot be converted. As result, the test fails as
expected. Chakra, in contrast, incorrectly converts the string to zero, making the test to pass.

So far, ten of the bugs we reported
were confirmed, two of which were fixed. One bug report we
submitted was rejected on the basis that the offending JS file
manifested an expected incompatibility across engine
implementations.
Note from the table that all bug
reports still waiting for confirmation are associated with the
JavaScriptCore engine (JSC). A closer look at the JSC issue tracker
showed that the triage process is very slow for that engine. As of
now, we did not find any new bug on SpiderMonkey and V8; the bugs we
found were duplicates and were not reported. Finally, it is
worth noting that 7 of the 17 JS files that manifested
discrepancies were \emph{not} produced with fuzzing (column
``Fuzz''). These are test files from suites of different engines. This
observation emphasizes the importance of continuously collecting test suites from
multiple sources; today, we use test suites from seven different open
source engines, including a total of 30K test files.

@@

%%  LocalWords:  d'Amorim oes Jornalista Fernandes JS Patra Pradel
%%  LocalWords:  fuzzer runtime WebAssembly's codebases Radamsa JSC
%%  LocalWords:  fuzzers linters JavaScriptCore SpiderMonkey AFL NUL
%%  LocalWords:  HonggFuzz jsfunfuzz Grammarinator WebAssembly ascii
%%  LocalWords:  valueOf unary NaN Chakra cccccc Url JavascriptCore
%%  LocalWords:  cgi tmp Cidade ToNumber LibFuzzer
